Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-19 snapshot_system/fast14_architecture.tex
modify

\section{Architecture and Implementation Details}
\label{sect:architecture}
Our system runs on a cluster of Linux machines with Xen-based VMs.
A distributed file system (DFS) manages  the physical disk storage and we use 
an open source DFS called QFS~\cite{QFS}. 
All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

\subsection{ Components of a cluster node } 
As  depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication component,
3) an append store client to store  and access snapshot data,
and 4)  a PDS client to support PDS index access.

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
has been modified since last backup. 
Segments are further divided into variable-sized chunks (average 4KB) 
using a content-based chunking algorithm~\cite{frame05}, 
which brings the opportunity of fine-grained deduplication.
When the VM issues a disk write, the dirty bit for the corresponding segment is set
and this indicates such a segments needs to be checked during snapshot backup. 
After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
[What happens with modification during snapshot backup stage.]

The representation of each snapshot has  a two-level index data structure.
The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
metadata of its chunks (called segment recipe).
In snapshot and segment recipes, 
the data structures  includes reference pointers to the actual data location to eliminate the need for additional indirection.

>>>>

\section{Architecture and Implementation Details}
\label{sect:architecture}
Our system runs on a cluster of Linux machines with Xen-based VMs and
an open-source package for the distributed file system  called QFS~\cite{QFS} to 
manages  the physical disk storage. 
All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

\subsection{ Components of a cluster node } 
As  depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication component,
3) an append store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called a \textit{segment}, indicating whether the segment
has been modified since last backup. 
Segments are further divided into variable-sized chunks (average 4KB) 
using a content-based chunking algorithm~\cite{frame05}, 
which brings the opportunity of fine-grained deduplication.
When the VM issues a disk write, the dirty bit for the corresponding segment is set
and this indicates such a segments needs to be checked during snapshot backup. 
After the snapshot backup is finished, the driver resets the dirty bit map to a clean state.
For data modification during snapshot backup stage, a copy-on-write scheme is set so that backup
still copies a frozen version while the modification can still carry on.

The representation of each snapshot has  a two-level index data structure.
The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
metadata of its chunks (called segment recipe).
In snapshot and segment recipes, 
the data structures  includes reference to the actual data location to eliminate the need for additional indirection.
